Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Rewrite look-like-nothing.

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Examples of look-like-nothing transports are
obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
Both obfs2 and obfs3 work by superenciphering
\vp{not clear here what superenciphering means; presumably, it's a reference
to encrypting a stream that's already encrypted, but the reader has to pause
and work that out}
an underlying stream,
using a key exchange that has no plaintext components.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in its
payload obfuscation, but additionally obscures its traffic signature
(packet lengths and timing), and is designed to resist active probing.
A ScrambleSuit server will accept a TCP connection but not send a reply
until the client proves knowledge of a shared secret.
\vp{Say, has there been any work on using port-knocking to resist active
probing?}
obfs4~\cite{obfs4}
(which despite the name has more in common with ScrambleSuit than with obfs2 and obfs3)
builds on ScrambleSuit with more efficient cryptography and an authenticated handshake.

>>>>

There are two general strategies for countering content-based blocking.
The first is to make traffic look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Following the first strategy are the so-called ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Examples of look-like-nothing transports are
obfuscated-openssh~\cite{obfuscated-openssh} and its string of successors:
obfs2~\cite{obfs2}, obfs3~\cite{obfs3}, ScrambleSuit~\cite{scramblesuit}, and obfs4~\cite{obfs4}.
They all work by re-encrypting
an underlying stream so that there remains no plaintext components,
not even in the handshake and key exchange.
obfs2, introduced in early 2012~\cite{obfsproxy-arms-race},
used a fairly weak key exchange that can be detected passively;
it is now deprecated and little used.
obfs3 is currently Tor's most-used transport~\cite{metrics-obfs3}.
It improves on obfs2 with a Diffie--Hellman key exchange,
public keys being encoded so as to be indistinguishable from random binary strings.
ScrambleSuit and obfs4 add resistance to active probing:
the server accepts a TCP connection but does not send a reply
until the client proves knowledge of a secret shared out of band.
They additionally additionally obscure the traffic signature of the underlying stream
by modifying packet lengths and timing.
